Live Functional Programming with Typed Holes

### 2018-02-08 intro.tex
cast errors

In live programming, we expect that programs will generally have holes
in both terms and types (CITE?); however, to understand the mechanisms
of \HazelnutLive, it is instructive to imagine situations where the
only holes are in terms, or are in types.
%
When we only use expression holes and no type holes, we do not need
type casts, or the other dynamic mechanisms of gradual typing.
% 
When we only use type holes, we recover gradual typing and do not need
indeterminate forms (except for cast errors, which we classify this
way).

>>>>

In live programming, we expect that programs will generally have holes
in both terms and types (CITE?); however, to understand the mechanisms
of \HazelnutLive, it is instructive to imagine situations where the
only holes are in terms, or are in types.
%
When we only use expression holes and no type holes, we do not need
type casts, or the other dynamic mechanisms of gradual typing.
% 
When we only use type holes, we recover gradual typing and do not use
indeterminate forms until and unless cast errors arise.

Cast errors as indeterminate forms:

Instead of being ``stuck'', cast errors in \HazelnutLive are
fully-reduced indeterminate terms.
